\section{Motivation}
When referring to citizens, one must be aware that there exists multiple different types of autism under the umbrella called \textit{the autism spectrum}.
Besides the widely different diagnosis covered by the autism spectrum, the degree or severity of a given disorder greatly affects the nature of any given citizen.
Because of this there rarely is one thing that defines all citizens hence the GIRAF project must accommodate many different use cases, scenarios and configurations.
However, one thing that seems to be consistent across the autism spectrum, is the need for structure and visual guidance.

The citizen's need for scheduling may seem excessive to some, but for citizens it is often necessary for them to handle their everyday activities.
In certain cases the scheduling needs to be upright pedantic in order for some citizens to complete even the simplest of tasks, e.g. taking a bath or using a toilet.
This is what the GIRAF project tries to help the citizens with.

Furthermore some citizens may not be able to cope with large visual objects.
Demands and specifications as these must also be thought into the design of GIRAF, if it aims to provide functionality to a majority of citizens.
For more information on the institutions work with the citizens and the citizen's needs, see the full notes from the presentation \cite{GIRAF20161stMeeting}.

In the following part we present the work done in the intial mini sprint of the project, which we call sprint 0.
This sprint deals with knowledge aquisition, aswell as agreeing on workflow in the multi-project.

\todo[inline]{Skal vi have noget mere omkring emnerne som er interessante for projektet i indledningen? - Workflow, existing code base, evt. goals of project}
\kim{Jeg er ikke sikker på hvad i mener med workflow, i skal skrive om jeres process og multiprojektets process. Hvis i kommer til at skulle refere tilbage til den nuværende version af kodebased så kunne det godt give mening at beskrive den her, men jeg ved ikke nok om jeres projekt endnu til at kunne udtale om det bliver relevant. 
Jeg synes ikke at i behøver at opstille nogle goals, medmindre at i gerne vil have nogle kriterier som i kan referer tilbage til når i laver beslutninger. Det kunne være at kode readability er vigtigt, derfor kan i retfærdiggøre at bruge til på at dokumentere ting. Igen jeg ved ikke nok om jeres projekt for at kunne udtage mig om det.}
