%draft1
\chapter{Introduction}
Autism Spectrum Disorder (\textbf{ASD}) often referred to simply as autism, is a 
group of neurodevelopmental disorders that often affects socialisation, communication and learning.
Treatment will often focuss on minimising the effects of the disorder in order to improve general quality of life as no cure exists.
% http://www.scielo.br/scielo.php?script=sci_arttext&pid=S1516-44462006000500002&lng=en&nrm=iso&tlng=en4bibtex
% http://pediatrics.aappublications.org/content/120/5/1162.abstract
This project is developed in collaberation between undergradute \todo{Skal vi bruge dette ord? - Troels} software students at Aalborg University and educational \todo{Er de alle sammen educational? - Troels} institutions located in Aalborg that all specialise in children with ASD.
The goal of the project is to provide these institution with software solutions for their caregivers that can aid them in helping those suffering from ASD.
In the collaboration process caretakers from each institution serves as the customer providing general knowledge of problem domain as well as requirements for the system.

The project, named GIRAF (Graphical Interface Resources for Autistic Folk), has been in development since it was started by Ulrik Nyman, Associate Professor at the department of Computer Science at Aalborg University, in 2011. 
Since then it has served as the bachelor project for software students, making this year its sixth iteration of software students.
The goal for the system is to provide a nonprofit and open-source software tool to help children suffering from ASD.

A total of 34 software students divided into nine groups will proceed with development of GIRAF.
Each group will have to work together in order to ensure the best outcome.
For all included this provides new challenges that have not been present in previous experience working on smaller projects in independent group environments.
Furthermore the inherited project already contains a large existing code base, unfamiliar to this years developers providing a further set of challenges.

\info[inline]{Skal vi have noget om at der traditionelt har været 4 sprints? At folk har arbejdet agilt? Statusen på kodebasen? - Troels}
\info[inline]{Vi har jo også adgang til de gamle rapporter, skal vi skrive noget om at der er gode råd at hente der? Og de ofte danner grund for de valg vi træffer? - Troels}