\subsection*{Workflow}
In this section we will introduce the workflow for collaboration in the Giraf project, under Scrum of Scrum. 
Groups takes on user stories on the sprint planning meeting, but can also remove or add more during the sprint.
This is also a result of task estimation taking place after claiming the user story, which can be problematic, since a group might take too many or too few user stories at the meeting and have to correct it later. 
If the estimation was done before claiming the user stories, then they might not be accurate as it is not certain that the same people who estimate it would end up doing the user story.
And if every group took part in estimating every task it would end up wasting a lot of time. 


Now that the tools and development method has been presented, we will present how these tools interact with the Scrum method used and also the Scrum of Scrums. \kim{Sounds confusion, please rephrase. Specifically I am unhappy with the ``used and also'' formulation.}
To do this we will show the workflow on a task from\kim{...of a task, starting from...} when it is introduced\kim{Are task really introduced? try to be more precise.} till\kim{-l} the task is considered completed through use of a flow diagram.
\kim{I just realized that you never defined what a task is. I am guessing that a user story contains several task or how does it work? However, you say that a backlog contains tasks as oppose to user stories. Please explain.}
Multiple tasks are chosen by each group of the multi-project for each sprint, but it is simpler to explain the workflow using only a single task. \kim{you alraedy said that on the line above.}
\kim{Try to add terms such as product backlog and sprint backlog.}
The aforementioned flow diagram is \myref{fig:workflow}. \kim{Aforementioned is properly one of my favorite words. It is AWESOME.}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[node distance = 0.5cm, auto]
	    \footnotesize
	    \node[wideblock]
	            (task) at (0,0)
	            {User story is introduced on Phabricator without a priority, either by a developer or the customer};
	        
	    \node[wideblock, below = of task]
	            (triage) {The PO of the multi-project give the user story a priority or discard it};
	            
	    \node[wideblock, below = of triage]
	            (planning) {User story is claimed by a project group on Phabricator};
	            
	    \node[wideblock, below = of planning]
	            (estimate) {The User Story is estimated by the project group};
	            
	    \node[wideblock, below = of estimate]
	            (branch) {A branch is created in git repository involving the user story, which uses the id of the user story};
	    
	    \node[wideblock, below = of branch]
	            (work) {The user story is completed and is ready for review, so a diff is created on Phabricator};
	            
	    \node[wideblock, below = of work]
	            (review) {A reviewer is chosen for the user story, and he/she reviews the diff and check if the user story is completed.};

	    \node[decision, below = of review]
	            (ready) {Changes?};


	    \node[wideblock, below = of ready]
	            (land) {The diff is applied to the master branch and the task is marked as completed on Phabricator};
	            
	    \path[line] (task) -- (triage);
	    \path[line] (triage) -- (planning);
	    \path[line] (planning) -- (estimate);
	    \path[line] (estimate) -- (branch);
	    \path[line] (branch) -- (work);
	    \path[line] (work) -- (review);
	    \path[line] (review) -- (ready);
	    \node[draw=none, right of = ready, node distance = 6.5cm] (cornerthree){};
	    \draw[-] (ready) -- node {yes} (cornerthree.center);
	    \path[line] (cornerthree.center) |- (work);
	    \path[line] (ready) -- node {no} (land);
	    
	\end{tikzpicture}
	\caption{Simplified workflow.}
	\label{fig:workflow}
\end{figure}
\kim{I like that you use tikz, being able to use tikz is a good skill to have.}
\kim{Where do tasks come from? I assume that they either originates from customers or developers. Actually I would assume that customers created user stories (or the product owners created them on their behalf) as oppose to tasks. }
\kim{What is this repository that you are talking about. This is the first time you mention a repository.}
\kim{I know that it is out of the scope of this workflow but how do you know how many tasks a group should put on their sprint backlog? }
\kim{How is a reviewer chosen?}
\kim{These are some of the questions I had after looking at the workflow diagram. I am not saying that you have to explain every little detail, you need to decide what is important and then make sure to explain that.}
\kim{Now that you have explained the workflow then I would like to know why you designed it this way. What pros and cons does it have? }
