\subsection{Wiki Migration}
Part of our responsibility as the ``Documentation and Wiki'' area of responsibility is to create a new wiki structure that can be used for the GIRAF project on Phabricator.
Additionally the old wiki on Redmine should be migrated to the new wiki on Phabricator. 

Firstly we read the contents of the old wiki, then we decided on what documents to migrate. 
Some documents are not migrated as they related to how to use Redmine. 
Most of the old guides can still provide some utility but may not be up-to date.
The documents we migrated without updating the contents to how we add a disclaimer: ``IMPORTANT: This wiki entry has not been update in 2016''.

We have created a new front page of the wiki, the purpose of this is to provide information and to link to other information on and off the wiki.
The front page contains the following contents: 

\begin{enumerate}
    \item Actionable Commitments
    \item Guides
    \item Goals
    \item Useful Links
    \item Sprint Dates
    \item Backlog
    \item Groups and Slack Channels
    \item Wordlist
\end{enumerate}

Most of the wiki contents is guides for various topics, these are the following made during this years GIRAF project:

\begin{itemize}
    \item Gradle upgrade guide
    \item Set up a project (In Phabricator)
    \item Task Creation Guideline (In Phabricator)
    \item Unit Test
    \item Using a consistent File Encoding
    \item Workflow guide (Git gud with GIRAF)
    \item Highlighting Code in WIKI
\end{itemize}
\bigskip
And the following are migrated from the old wiki:

\begin{itemize}
	\item Android Studio Setup
    \item Android Guide And Guidelines
    \item App and library renaming in Android Studio
    \item Continuous Integration Guidelines
    \item Git Guide
    \item Codestyle CheckStyle
    \item Dependency Management
    \item Development Method
    \item Google Analytics
    \item How to use Google Play
    \item How to implement the pictosearch library
    \item Javadocs
    \item Testing
\end{itemize}

\unsure[inline]{Bliver dette for meget? - Troels}
\unsure[inline]{Skal der forklares hvordan konverteringen forgik? Alså Redmine ``markdown'' til det Phabricator bruger. - Troels}
