\chapter{Sprint Planning}\label{chap:Planning4}
For the fourth and last sprint, the sprint planning was held on Thursday the 5th of may.
Originally it was planned that the fourth sprint should end a week before the reports are due, i.e. 19th of May, however at the sprint planning meeting PO and Scrum Masters revealed that the sprint was to end on the 15th of may instead.
Within this time frame we allocate 48 EP to be available during the sprint.
This chapter describes how these EP are expected to be spent, and what tasks we will be working on.

\section{Sprint Backlog}
As is evident from \myref[name]{sec:sprintreview3} we did not completely finish the REST API user stories pertaining to Week Schedule and Sequence despite spending significantly more EP than we had allocated.
Last sprint we decided to leave two user stories on the sprint backlog for this sprint to be finished, this sprint will in part revolve around finishing up these user stories.
In the previous sprint we ended up spending all our allocated EP and more on developing the REST API, as such documentation for this is currently lacking in the report and therefore we will also spend a significant amount of EP on documenting the REST API.
As part of this documentation we will also solve another user story that should prepare next years students on how to continue to development of the REST API, what is missing, how to get started and similar things that we spent a lot of time on.
This leaves us with four primary objectives which we will spend our time on, one of them being documentation for the work we did in our third sprint and the remaining three being the following user stories:

\begin{center}
\userstory{As a developer I would like an endpoint for Week Schedules, such that I can retrieve them from the GIRAF REST API.}
\medskip
\userstory{As a developer I would like an endpoint for Sequences, such that I can retrieve them from the GIRAF REST API.}
\medskip
\userstory{As a future developer I would like a guide for developing on the REST API, along with a plan for what has been created for the API and what still needs to be implemented, such that I can quickly get an overview and set up my work environment at the start of the project.}
\end{center}

\bigskip
Since we have already invested a significant amount of time in the development of the REST API, we have a fairly good idea of how many EP the two REST API tasks will require, as such we estimate 6 EP for each of the endpoints to be developed.
This is based on the general knowledge we have gained in regards to developing the REST API, as well as having a fully defined design, and two already implemented and tested layers.%*Salute* General Knowledge!
For the third user story we estimate 8 EP.
Combined this amounts to 20 EP estimated on user stories, the remaining EP will be spent on our report and documentation of the work done in our third sprint as well as documenting the work which we will do in this sprint.
