\chapter*{Preface\markboth{Preface}{Preface}} \addcontentsline{toc}{chapter}{Preface}
This report have been written by four software students at Aalborg University as their bachelor project.
In the report \enquote{we} refers to the authors of the paper, unless otherwise stated.
We thank the other groups in the multi--project, especially group SW615F16 which we have worked closely with.
We would also like to thank our supervisor Kim A. Jakobsen for his advice during the semester.

In the report we use \texttt{this monospaced font}, when we talk about specific instances of classes, variables or programming constructs.
We do this to avoid ambiguity, e.g. since \texttt{WeekSchedule}, week schedule and Week Schedule, refers to three different things, namely a class, a concept and an app.
We assume that the reader has experience or knowledge of programming in Java.
Additionally this report should be viewed in color.


\vspace{\baselineskip}\hfill Aalborg University, \today
\vfill\noindent
\begin{minipage}[b]{0.45\textwidth}
    \centering
    \rule{\textwidth}{0.5pt}\\
    Mathias Sass Michno\\
    {\footnotesize
    \href{mailto:mmichn13@student.aau.dk}{<mmichn13@student.aau.dk>}}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
    \centering
    \rule{\textwidth}{0.5pt}\\
    Marc Tom Thorgersen\\
    {\footnotesize     \href{mailto:mthorg13@student.aau.dk}{<mthorg13@student.aau.dk>}}
\end{minipage}\\\vspace{2\baselineskip}

\vspace{50pt}

\noindent
\begin{minipage}[b]{0.45\textwidth}
    \centering
    \rule{\textwidth}{0.5pt}\\
    Troels Beck Krøgh\\
    {\footnotesize \href{mailto:tkragh13@student.aau.dk}{<tkragh13@student.aau.dk>}}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
    \centering
    \rule{\textwidth}{0.5pt}\\
    Søren Hvidberg Frandsen\\
    {\footnotesize \href{mailto:sfrand12@student.aau.dk}{<sfrand12@student.aau.dk>}}
\end{minipage}\\
